Fail Faster

### 2025-03-23 paper/paper.tex
blah

The type-deriving algorithm follows a compositional pattern. Generators for complex types 
are synthesized by structurally composing generators of their subtypes: 
base types are mapped to primitive generators included in the generator library;
product types---such as tuples and records---are handled by sampling each component 
using \texttt{bind} and aggregating the results; sum types, or variants, are generated using 
a \texttt{weighted\_union} of the generators for each case; and for recursive types, 
the entire generator is wrapped in a fixed-point combinator, and a recursive handle 
is used as the component generator for all recursive occurrences of the type.
This compositional approach maps naturally to staged generation: 
to derive a staged generator, we replace each standard combinator 
with its staged counterpart. The derivation algorithm remains unchanged.

>>>>

The type-deriving algorithm follows a compositional pattern. Generators for complex types 
are synthesized by structurally composing generators of their subtypes: 
base types are mapped to primitive generators included in the generator library;
product types---such as tuples and records---are handled by sampling each component 
using \texttt{bind} and aggregating the results; sum types, or variants, are generated using 
a \texttt{weighted\_union} of the generators for each case; and for recursive types, 
the entire generator is wrapped in a fixed-point combinator, and a recursive handle 
is used as the generator for all recursive occurrences of the type.
This compositional approach maps naturally to staged generation: 
to derive a staged generator, we replace each standard combinator 
with its staged counterpart. The derivation algorithm remains unchanged.
